\section{Behavior}
To work together well as a team the way that we behave towards each other is a very important factor. Therefore, we will adhere to the agreements provided below on how we behave towards each other and what to do when this does not work out. 
\\\\
We try to always treat our teammates with respect and keep it friendly. But when a situation calls for a less friendly tone, we still keep the conversations respectful.  
\\\\
We always behave appropriately towards each other and never make a person feel excluded from the group.  
\\\\
When something needs to be said to another person, do this in the correct context. Meaning when something more private needs to be discussed, do this in private and when something needs to be discussed with the entire group, discuss it with the entire group. 
\\\\
Upon the arrival of a disagreement, we first try to resolve this by meeting in person. This could mean first trying to get to an agreement on the problem, otherwise we could try to vote on a solution and the solution with the most votes wins. A situation could still arise in which this would not be a good solution for the current situation, or a person is not listening to what the rest of the team says. In this case, we will turn to our Teaching Assistant (TA) to help with the heated situation. The TA is a neutral party that can be very helpful in these types of situations. 
\\\\
Because of ever-changing circumstances, we understand that conflicts may arise so when we as a team realize that something has gone suboptimal, we will reflect on that and find ways to avoid this in the future. 
