\section{Communication}
When working in a team, communication is one of the most important aspects. In the case of this project, several platforms will be used to ensure the proper transfer of information and/or files between team members. Firstly, the Mattermost channels provided by the university will be used for all official communication. This includes feedback regarding behavior, work ethic or commitment, communication with our assigned TA (Mike Segers), and any other information we deem important enough to put on record. After a mandatory meeting, the notes will be uploaded on GitLab. After any other offline meeting, an update will be sent to the TA to inform them of our progress and our plans. Any feedback regarding merge requests should be given directly on GitLab by the assigned reviewer in a constructive manner (specifying what is good and what could be improved).
\\\\
The other major platforms used for communication between members are Discord and WhatsApp. Organizing meetings outside of the mandatory ones or giving small updates to the other team members should be done on WhatsApp, as well as asking casual questions that do not require the help of a TA or another form of authority. Discord will be the main way of holding online meetings. File sharing will preferably also be done on Discord, however, if not possible WhatsApp is a good alternative.
\\\\
During meetings, online or offline, the team members should try their best to include everyone in the conversation and to be transparent with each other. Everyone should try to give their input as much as possible but also listen to what the others have to say. 
