\section{Consequences}
Some actions that members of the team do, may have consequences. The most prominent one is, of course, being late at a meeting. For the aforementioned meeting with the TA (Teaching Assistant). Being too late for this meeting will make you marked as absent, having more than one of these absent marks will result in an immediate failure of the course. For being late at an external meeting, the consequence would be buying a round of beers at the /pub.
\\\\
If a person is absent from external meetings on a regular basis, without any good reason and is also doing just the bare minimum of work (just enough so he does not fail), while the other members of the team are active and contribute a lot more to the project, then the TA will be involved. 
Apart from being late, other actions also have consequences, not meeting deadlines set by the teams without a reasonable excuse would fall under a case-by-case consequence, this being dependent on further context. Never should a consequence be in the form of doing extra work for the team, as this would only “snowball” the member of the team to meet less deadlines. Additionally, as stated before, a consequence should never include verbal or physical harassment. Members of the team should try their best to keep consequences civil and well-mannered.
\\\\
For any other issues that might arise, the person who caused them will have to explain to the others why he did that and further action will be taken based on the discussion he will have with the team.
